%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same
% directory as this .tex file. These files provide the resume style and themes
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{amsmath}
\usepackage[utf8]{inputenc}

\usepackage[scale=0.85]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

\usepackage{fontawesome5}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Abel} % Your first name
\familyname{Guada Azze} % Your last name

% All information in this block is optional, comment out any lines you don't need
%\title{Curriculum Vitae}
%\address{2 rue Fran\c cois Verny}{Brest, France 29806}
%\mobile{(+34) 6 72 33 04 26}
%\phone{(000) 111 1112}
%\fax{(000) 111 1113}
%\email{abel.guada@cunef.edu}
%\social[linkedin][https://www.linkedin.com/in/abel-guada-azze-5625211aa/]{abel-guada-azze}
% \email{aguada@est-econ.uc3m.es}
%\homepage{staff.org.edu/~jsmith}{staff.org.edu/$\sim$jsmith} % The first argument is %the url for the clickable link, the second argument is the url displayed in the %template - this allows special characters to be displayed such as the tilde in this %example
%\extrainfo{additional information}
%\photo[70pt][0.4pt]{picture} % The first bracket is the picture height, the second is %the thickness of the frame around the picture (0pt for no frame)
\quote{Last update on July, 2025}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}
\cventry{2018-2023}{PhD in Mathematical Engineering}{Carlos III University of Madrid}{}{}{PhD thesis: ``Optimal Stopping of Gauss-Markov processes'', supervised by professors Bernardo D'Auria and Eduardo García Portugués.}
\cventry{2016--2018}{MSc in Mathematical Engineering}{Carlos III University of Madrid}{}{}{MSc thesis: "Inferring the optimal stopping boundary for a Brownian bridge", supervised by professors Bernardo D'Auria and Eduardo García Portugués.}
\cventry{2010--2014}{BSc in Mathematics}{University of Havana}{}{}{BSc thesis: "Selección del ancho de banda en
estimación por Kernel para colas pesadas", supervised by professor Luis A. Salomón.}  % Arguments not required can be left empty

%----------------------------------------------------------------------------------------
%	Positions
%----------------------------------------------------------------------------------------

\section{Positions}
\cventry{2023+}{Associate Professor}{Department of Quantitative Methods}{CUNEF University}{}{}
\cventry{2023-2023}{Graduate Teaching Assistant}{Department of Statistics}{Carlos III University of Madrid}{}{}
\cventry{2018-2023}{Research Assistant}{Department of Statistics}{Carlos III University of Madrid}{}{}
\cventry{2022-2022}{Visiting PhD researcher}{Department of Economics}{Università "G. d'Annunzio" Chieti-Pescara}{}{}
\cventry{2014-2016}{Graduate Teaching Assistant}{Department of Mathematics}{Technological University of Havana José Antonio Echeverría}{}{}

%----------------------------------------------------------------------------------------
%	AWARDS
%----------------------------------------------------------------------------------------

\section{Awards}
\cventry{2014}{Roberto Peña award}{conceded by the Cuban Society of
Mathematics and Computer Science for the work "Estimación por Kernel para Colas Pesadas"}{}{}{}
\cventry{2014}{Gran Premio}{conceded by the Department of Mathematics and Computer Science of the University of Havana for the work "Estimación por Kernel para Colas Pesadas"}{}{}{Top of my year in the \textit{Jornada Científica Estudiantil} 2014 of the University of Havana.}
\cventry{2013}{Relevante 3ro Matemática Aplicada}{conceded by the Department of Mathematics and Computer Science of the University of Havana for the work "Estimación por Kernel en muestras pequeñas"}{}{}{Top of my year in the category of applied mathematics in the \textit{Jornada Científica Estudiantil 2013} of the University of Havana.}

%----------------------------------------------------------------------------------------
%	RESEARCH PROJECTS
%----------------------------------------------------------------------------------------

\section{Research projects and grants}
% \cventry{01/09/2021 28/02/2025}{PID2020-116694GB-I00}{Optimización bajo incertidumbre y control estocástico: aplicaciones a mercados
% estocásticos en el paradigma del Big Data}{Principal researcher: PhD. Carlos Ruiz Mora (Universidad
% Carlos III de Madrid)}{Grant: 61.710 €}{}

\section{Scholarships}
\cventry{2018-2022}{Scholarship for PhD studies}{given by Carlos III University of Madrid}{}{}{}
\cventry{2016-2018}{Scholarship for MSc studies}{given by Carlos III University of Madrid}{}{}{}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------

\section{Publications}

\subsection{Working papers}
\cvitem{2026}{Azze A, D'Auria B, Ferrari G. Robust Ergodic Control of Jump-Diffusion Systems under Drift and Intensity Uncertainty. arXiv. \url{}}
\cvitem{2025}{Azze A, D'Auria B. On the optimal stopping of Gauss-Markov bridges with random pinning points. arXiv. \url{https://doi.org/10.48550/arXiv.2505.03636}}

\subsection{Refereed papers}
\cvitem{2025}{Azze A, D'Auria B, García-Portugués E. Optimal stopping of Gauss--Markov bridges. Advances in Applied Probability. 2025;57(1):1-34. \url{https://doi.org/10.1017/apr.2024.21}}
\cvitem{2024}{Azze, A., D'Amico, G., D'Auria, B. et al. Modelling a storage system of a wind farm with a ramp-rate limitation: a semi-Markov modulated Brownian bridge approach. Ann Oper Res 345, 39--57 (2025). \url{https://doi.org/10.1007/s10479-024-06236-6}}
\cvitem{2024}{Azze, Abel., D'Auria, Bernardo., and García--Portugués, Eduardo. Optimal exercise of American options under time-dependent Ornstein--Uhlenbeck processes. Stochastics. 2024; 96(1), 921-946. \url{https://doi.org/10.1080/17442508.2024.2325402}}
\cvitem{2024}{Azze, Abel., D'Auria, Bernardo., and García-Portugués, Eduardo. Optimal stopping of an Ornstein--Uhlenbeck bridge. Stochastic Processes and their Applications. 2024; 172, Art. 104342. \url{https://doi.org/10.1016/j.spa.2024.104342}}
\cvitem{2020}{D'Auria, Bernardo and Garc\'ia-Portugu\'es, Eduardo and Guada, Abel. Discounted optimal stopping of a Brownian bridge, with application to American options under pinning. Mathematics. 2020; 8(7):1159. \url{doi:10.3390/math8071159}}


\subsection{Preprints}

%----------------------------------------------------------------------------------------
%	THESIS
%----------------------------------------------------------------------------------------

\section{Thesis Advisor}

\subsection{Bachelor}

\subsection{MSc}

\cventry{2024--2025}{MSc in Big Data Analytics}{Universidad Carlos III de Madrid}{}{}{
Title: Optimal stopping of a Brownian bridge with a random pinning point \\
Authors: Manuel Emilio Baliño Vilar \\
Supervisors: Eduardo García Portugués and Abel Guada Azze.}

\cventry{2023--2024}{MSc en Ciencia de Datos}{CUNEF Universidad}{}{}{
Title: Perfilado de clientes \\
Authors: Guzmán Muñoz Revuelta and Gaspar Cólogan Barajas \\
Supervisors: Abel Guada Azze (academic supervision), and Pablo Jimenez Ruiz and Pablo Corral Vila (institutional supervision).}



%----------------------------------------------------------------------------------------
%	TEACHING
%----------------------------------------------------------------------------------------

\section{Teaching}

\subsection{Theory}

\cventry{2024/2025}{Quantitative Methos for Humanities}{Bachelor in Philosophy, Politics, and Economics}{CUNEF Univsersidad}{}{}
\cventry{2023/2024}{Econometría}{Doble Grado en Administración y Dirección de Empresas e Ingeniería Informática}{CUNEF Univsersidad}{}{}

\cventry{2024/2025}{Mathematics}{Bachelor in Philosophy, Politics, and Economics}{CUNEF Univsersidad}{}{}
\cventry{2024/2025}{Data Collection and Processing}{Double Bachelor in Business Administration and Law}{CUNEF Universidad}{}{}

\cventry{2023/2024}{Estadística Empresarial II}{Bachelor in Business Administration}{CUNEF Centro Adscrito}{}{}
\cventry{2023/2024}{Econometría}{Doble Grado en Administración y Dirección de Empresas e Ingeniería Informática}{CUNEF Univsersidad}{}{}
\cventry{2023/2024}{Econometrics}{Double Bachelor in Business Administration and Law}{CUNEF Univsersidad}{}{}

\cventry{2023/2024}{Data Collection and Processing}{Double Bachelor in Business Administration and Law}{CUNEF Universidad}{}{}
\cventry{2023/2024}{Mathematics}{Bachelor in Philosophy, Politics, and Economics}{CUNEF Univsersidad}{}{}

\cventry{2022/2023}{Analysis of dynamic data}{Bachelor in Finance and Accounting}{Carlos III University of Madrid}{}{}
\cventry{2022/2023}{Statistical methods for social sciences: prevision techniques}{Bachelor in International Studies and Business Administration}{Carlos III University of Madrid}{}{}

\subsection{Practices}
\cventry{2022/2023}{Statistical methods for social sciences: prevision techniques}{Bachelor in International Studies and Business Administration}{Carlos III University of Madrid}{}{}
\cventry{2022/2023}{Statistical Learning}{Bachelor in Data Science and Engineering}{Carlos III University of Madrid}{}{}
\cventry{2021/2022}{Statistics for social sciences I}{Bachelor in Political Science}{Carlos III University of Madrid}{}{}
\cventry{2021/2022}{Probability and Data Analysis}{Bachelor in Data Science and Engineering}{Carlos III University of Madrid}{}{}
\cventry{2020/2021}{Procesos estocásticos}{Bachelor in Statistics and Business}{Carlos III University of Madrid}{}{}
\cventry{2020/2021}{Procesos estocásticos}{Bachelor in Statistics and Business}{Carlos III University of Madrid}{}{}
\cventry{2019/2020}{Procesos estocásticos}{Bachelor in Statistics and Business}{Carlos III University of Madrid}{}{}
\cventry{2018/2019}{Estadística}{Bachelor in Electric Engineering}{Carlos III University of Madrid}{}{}
\cventry{2018/2019}{Statistics}{Bachelor in Communication Systems Engineering}{Carlos III University of Madrid}{}{}
\cventry{2018/2019}{Statistics}{Bachelor in Automatic and Industrial Engineering}{Carlos III University of Madrid}{}{}
\cventry{2015/2016}{Probabilidades y estadística}{Bachelor in Civil Engineering}{Technological University of Havana José Antonio Echeverría}{}{}
\cventry{2015/2016}{Matemática III para arquitectos}{Bachelor in Architecture}{Technological University of Havana José Antonio Echeverría}{}{}
\cventry{2014/2015}{Probabilidades y estadística}{Bachelor in Civil Engineering}{Technological University of Havana José Antonio Echeverría}{}{}
\cventry{2014/2015}{Matemática I}{Bachelor in Civil Engineering}{Technological University of Havana José Antonio Echeverría}{}{}

%----------------------------------------------------------------------------------------
% SEMINARS CONTRIBUTIONS
%----------------------------------------------------------------------------------------

\section{Seminar contributions (speaker underlined)}

\cventry{26/03/2025}{``Optimally Stopping a Gauss-Markov process with random terminal value''}{Probability Seminar}{Department of Mathematics, University of Manchester, UK.}{\underline{Abel Azze}, Bernardo D'Auria}{}
\cventry{20/12/2023}{``Optimal stopping of Gauss-Markov processes''}{Quantitative Methods job market seminar}{Department of Quantitative Methods, CUNEF Universidad, Spain.}{\underline{Abel Azze}, Bernardo D'Auria}{}

%----------------------------------------------------------------------------------------
% CONFERENCE and POSTER CONTRIBUTIONS
%----------------------------------------------------------------------------------------

\section{Conference contributions (speaker underlined)}

\subsection{Invited talks}
\cventry{12/09/2025 14/09/2025}{``Optimal stopping of Gauss-Markov processes with random terminal value
''}{Fields-CFI Conference on Optimal Stopping and Its Applications in Finance and Insurance}{The Fields Institute, Toronto, Canada}{\underline{Abel Azze}, Bernardo D'Auria}{}

\subsection{Contributed talks}
\cventry{23/09/2024 25/09/2024}{``Optimal stopping of Gauss-Markov bridges''}{4th International Workshop on Stochastic Processes and their Applications}{Universidad de Zaragoza, Zaragoza}{\underline{Abel Azze}, Bernardo D'Auria, and Eduardo García-Portugués}{}
\cventry{08/07/2024 12/07/2024}{``Optimal stopping of Gauss-Markov bridges with applications to American options''}{12th Bachelier World Congress of the Bachelier Finance Society}{FGV EMAp, Rio de Janeiro}{\underline{Abel Azze}, Bernardo D'Auria, and Eduardo García-Portugués}{}
\cventry{13/11/2023 16/11/2023}{``Optimal stopping of Gauss--Markov bridge''}{Bringing Young Mathematicians Together (BYMAT) 2023}{ICMAT, Madrid}{\underline{Abel Azze}. Bernardo D'Auria, and Eduardo García-Portugués}{}

\cventry{13/01/2020 17/01/2020}{"Optimal exercise for American options under pinning effect"}{Theory and Practice of Optimal Stopping and Free Boundary Problems}{University of Leeds}{Bernardo D'Auria, Eduardo García-Portugués, and \underline{Abel Guada}}{}
\cventry{05/06/2019 07/06/2019}{"Optimal exercise for American options under stock pinning"}{2nd Spanish Young Statisticians and Operational Researchers Meeting (SYSORM 2019)}{Bernardo D'Auria, Eduardo García-Portugués, and \underline{Abel Guada-Azze}}{}{}
\cventry{04/04/2018 06/04/2018}{"Optimal stopping and Volterra type equations: application to the Brownian Bridge"}{Mathematical and Statistical Methods for Actuarial Sciences and Finance (MAF 2018)}{Bernardo D'Auria, Eduardo García-Portugués, and \underline{Abel Guada-Azze}}{}{}
\cventry{2014}{"Bandwith selection for heavy-tailed distributions"}{XXIV Encuentro de Estadísticos Cuba-México}{Havana, Cuba}{Luis A. Salomón and \underline{Abel Guada Azze}}{}
\cventry{2014}{"Estimación por Kernel para Colas Pesadas"}{Jornada Científica Estudiantil 2014 of the University of Havana}{Luis A. Salomón and \underline{Abel Guada Azze}}{}{}
\cventry{2013}{"Estimación por Kernel en muestras pequeñas"}{Jornada Científica Estudiantil 2013 of the University of Havana}{Luis A. Salomón and \underline{Abel Guada Azze}}{}{}
\subsection{Posters}
\cventry{2018}{"Inferring the optimal stopping boundary for a Brownian bridge"}{Statistical Methods for Big Data (SMBD 2018)}{Bernardo D'Auria, Eduardo García-Portugués, and \underline{Abel Guada-Azze}}{}{}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS
%----------------------------------------------------------------------------------------

\section{Referee}
\cvitem{2024}{Statistics and Probability Letters}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS
%----------------------------------------------------------------------------------------

\section{Computer skills}
\cvitem{Interpreted languages}{R, Mathematica, MATLAB, Python}
\cvitem{Compiled languages}{\TeX}
\cvitem{Other softwares}{RStudio, TeXstudio, GitHub, Mendeley, Zotero, JabRef}

%----------------------------------------------------------------------------------------
%	LANGUAGES
%----------------------------------------------------------------------------------------

\section{Languages}
\cvitemwithcomment{Spanish}{Native}{}
\cvitemwithcomment{English}{Advanced (C1)}{Qualification: Cambridge English Level 2 Certificate in ESOL International}

%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

%\clearpage

%\recipient{HR Departmnet}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

%\makelettertitle % Print letter title

%\lipsum[1-3] % Dummy text

%\makeletterclosing % Print letter signature

%----------------------------------------------------------------------------------------

\end{document}
